The SMT Competition 2015--2018

### 2019-04-15 2018/report/SMT-COMP.tex
Report: Addressed todo for sat/unsat tables

We only consider the \maintrack here, which contains a mixture of problems that
are satisfiable and unsatisfiable.
\todo{give numbers in percent for years or refer to table where the numbers should be: {table:benchmarks-main-track}}
For the \apptrack, this analysis is less meaningful since a benchmarks usually
contains a multitude of both satisfiable and unsatisfiable incremental queries
(which may depend on each other).
For the \ucoretrack, only known unsatisfiable benchmarks from the \maintrack
are used, which renders this analysis useless for this track.

>>>>

We only consider the \maintrack here, which contains a mixture of problems that
are satisfiable and unsatisfiable. A percentage of satisfiable, unsatisfiable
and unknown status benchmarks per division and year is given in
Table~\ref{table:benchmarks-main-track}.  For the \apptrack, this analysis is
less meaningful since a benchmarks usually contains a multitude of both
satisfiable and unsatisfiable incremental queries
(which may depend on each other).
For the \ucoretrack, only known unsatisfiable benchmarks from the \maintrack
are used, which renders this analysis useless for this track.
